### 2016-06-30 conclusions.tex
New conclusions

\label{sec:conclusions}
%Given the need for low-cost, easy to configure, testbeds that enable
%reproducible results, we provide a in-depth description of Aalborg
%University's \ac{Raspi} testbed and how to guarantee replicable
%results and managing scaling of the system.  We also provide a
%performance evaluation for network coding schemes, focusing on
%processing speed and energy behaviour for two \ac{Raspi} models,
%including algorithms that exploit \ac{SIMD} instructions and multicore
%capabilities of the \ac{Raspi} 2. Our measurements show that
%processing speeds of more than 80 Mbps and 800 Mbps are attainable for
%the \ac{Raspi} model 1 and 2, respectively, for a wide range of
%network coding configurations and maintaining a processing energy
%below 1 nJ/bit (or even an order of magnitude lower) in similar
%configurations. Future work in the use of \ac{Raspi} devices will
%focus on expanding the setup and automation of tasks to run the
%testbed, configure specified network topologies (e.g., with specific
%connectivity or packet loss ratios), reserve the use of these
%sub-networks for running tailored experiments, and opening the use of
%the testbed beyond our team at Aalborg University.

>>>>

\label{sec:conclusions}
OBsersving the expectation of the \ac{IoT} and lack for a low-cost, easy to configure testbed that enable reproducible results for mechanisms to address problems in this are, we provide a in-depth description of the new Aalborg University's \ac{Raspi} testbed and how to guarantee replicability and scaling managing of the system. The description shows how to set up interconnected \ac{Raspi}s with small SD cards for local storage, a Raspberry distro image, network connectivity and proper system administration privileges. The exposed work will permit researchers to replicate setups and scenarios for evaluating their strategies in a rapid and administrable way. Future work in the use of \ac{Raspi} devices will focus on expanding the setup and automation of tasks to run the testbed, configure specified network topologies (e.g., with specific connectivity or packet loss ratios), reserve the use of these sub-networks for running tailored experiments and opening the use of the testbed beyond our team at Aalborg University.
